What makes musicians infer teaching intentions?

### 2022-03-30 paper/manuscript.Rmd
remove spearman's tests
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

@@

## Correlation
A Pearson product-moment correlation coefficient was computed by default for correlation analysis and a Spearman's rank correlation coefficient was additionally computed if normality assumption was violated based on the Shapiro-Wilk normality test.

### Tempo (IOIs)
Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_art$p.value))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-1}*). Participants tended to identify slower performances as teaching.

However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (*p* `r if(ioi_dyn_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_dyn_norm_performance$p.value))}`). Therefore, a Spearman's rank correlation coefficient was additionally used to assess the relationship between performance tempi of dynamics recordings and participants' judgments. The result failed to reach significance (*r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`), suggesting that we need to be careful about the interpretation of the relationship between the performance tempi of dynamics recordings and participants' judgments as teaching.

@@

For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`, Piano; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`, *Figure \ref{fig:kot-1}*, right). The Shapiro-Wilk normality test revealed that the distribution of KOT for dynamics recordings was not normally distributed (Forte; *p* `r if(kot_for_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', kot_for_norm_performance$p.value))}`, Piano; *p* `r if(kot_pia_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', kot_pia_norm_performance$p.value))}`). Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for_spearman$estimate))`, *p* `r if(cor_kot_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for_spearman$p.value))}`, Piano; *r(`r cor_kot_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia_spearman$estimate))`, *p* `r if(cor_kot_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia_spearman$p.value))}`).

@@

For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r(`r cor_vel_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-1}*, left). The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings (legato parts) was not normally distributed (*p* `r if(vel_leg_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_leg_norm_performance$p.value))}`). A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg_spearman$estimate))`, *p* `r if(cor_vel_leg_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg_spearman$p.value))}`).

@@

For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ltos$p.value))}`, From Staccato to Legato; *r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_stol$p.value))}`, *Figure \ref{fig:vel-diff-1}*, left). The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings (transition points from legato to staccato) was not normally distributed (*p* `r if(vel_diff_ltos_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ltos_norm_performance$p.value))}`). A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for the transition points from legato to staccato and participants' judgments as teaching (*r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos_spearman$estimate))`, *p* `r if(cor_vel_diff_ltos_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ltos_spearman$p.value))}`).

@@

## Multiple regression

In order to further explore which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted. Statistical model assumptions were tested using the *performance* R package [@ludecke_2021] and most of the assumptions (see *Supplementary Material* for details) were met. Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs. staccato, forte vs. piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in *Data analysis*).

@@

## Correlation
As Experiment 1, a Pearson product-moment correlation coefficient was computed by default for correlation analysis and a Spearman's rank correlation coefficient was additionally computed if normality assumption was violated based on the Shapiro-Wilk normality test.

### Tempo (IOIs)
Unlike Experiment 1, there was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_ioi_art$p.value))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-2}*). Participants tended to identify slower performances as teaching for dynamics recordings.

However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (*p* `r if(ioi_dyn_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_dyn_norm_performance$p.value))}`). A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (*r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`), suggesting that we need to be careful about the interpretation of the relationship between the performance tempi of dynamics recordings and participants' judgments as teaching.

@@

### Dynamics (KV)
As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-2}*, right). Specifically, performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_pia$p.value))}`) were more likely to be judged as teaching. The Shapiro-Wilk normality test revealed that the distribution of KV values for dynamics recordings was not normally distributed (Forte; *p* `r if(vel_for_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_for_norm_performance$p.value))}`, Piano' *p* `r if(vel_pia_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_pia_norm_performance$p.value))}`). Spearman's rank correlation coefficient also confirmed that performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for_spearman$estimate))`, *p* `r if(cor_vel_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for_spearman$p.value))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_pia_spearman$p.value))}`) were more likely to be judged as teaching.

@@

### Dynamics contrast (KV-Diff)
As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (*Figure \ref{fig:vel-diff-2}*, right). Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`). The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; *p* `r if(vel_diff_ftop_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', vel_diff_ftop_norm_performance$p.value))}`, Piano to Forte; *p* `r if(vel_diff_ptof_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ptof_norm_performance$p.value))}`). Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop_spearman$estimate))`, *p* `r if(cor_vel_diff_ftop_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop_spearman$p.value))}`, Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof_spearman$estimate))`, *p* `r if(cor_vel_diff_ptof_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ptof_spearman$p.value))}`).

@@

## Multiple regression

As Experiment 1, we performed multiple regression analyses to further explore which feature of performance contributed the most to participants' judgments as teaching. Statistical model assumptions were tested and most of the assumptions (see *Supplementary Material* for details) were met. Again, since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs. staccato, forte vs. piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in *Data analysis* in Experiment 1).

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

## Correlation
### Tempo (IOIs)
Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_art$p.value))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-1}*). Participants tended to identify slower performances as teaching.

@@

For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`, Piano; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`, *Figure \ref{fig:kot-1}*, right).

@@

For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r(`r cor_vel_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-1}*, left).

@@

For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ltos$p.value))}`, From Staccato to Legato; *r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_stol$p.value))}`, *Figure \ref{fig:vel-diff-1}*, left).

@@

## Multiple regression
In order to further explore which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted. Statistical model assumptions were tested using the *performance* R package [@ludecke_2021] and most of the assumptions (see *Supplementary Material* for details) were met. Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs. staccato, forte vs. piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in *Data analysis*).

@@

## Correlation
### Tempo (IOIs)
Unlike Experiment 1, there was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_ioi_art$p.value))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-2}*). Participants tended to identify slower performances as teaching for dynamics recordings.

@@

### Dynamics (KV)
As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-2}*, right). Specifically, performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_pia$p.value))}`) were more likely to be judged as teaching.

@@

### Dynamics contrast (KV-Diff)
As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (*Figure \ref{fig:vel-diff-2}*, right). Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).

@@

## Multiple regression
As Experiment 1, we performed multiple regression analyses to further explore which feature of performance contributed the most to participants' judgments as teaching. Statistical model assumptions were tested and most of the assumptions (see *Supplementary Material* for details) were met. Again, since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs. staccato, forte vs. piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in *Data analysis* in Experiment 1).

### 2022-03-30 paper/manuscript.tex
remove spearman's tests
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

A Pearson product-moment correlation coefficient was computed by default for correlation analysis and a Spearman's rank correlation coefficient was additionally computed if normality assumption was violated based on the Shapiro-Wilk normality test.

@@

However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (\emph{p} = 0.037). Therefore, a Spearman's rank correlation coefficient was additionally used to assess the relationship between performance tempi of dynamics recordings and participants' judgments. The result failed to reach significance (\emph{r(46)} = .27, \emph{p} = 0.066), suggesting that we need to be careful about the interpretation of the relationship between the performance tempi of dynamics recordings and participants' judgments as teaching.

@@

For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r(46)} = -.04, \emph{p} = 0.81, Piano; \emph{r(46)} = -.19, \emph{p} = 0.19, \emph{Figure \ref{fig:kot-1}}, right). The Shapiro-Wilk normality test revealed that the distribution of KOT for dynamics recordings was not normally distributed (Forte; \emph{p} \textless{} 0.001, Piano; \emph{p} \textless{} 0.001). Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r(46)} = .15, \emph{p} = 0.31, Piano; \emph{r(46)} = -.12, \emph{p} = 0.43).

@@

For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r(46)} = .10, \emph{p} = 0.52, Staccato; \emph{r(46)} = -.02, \emph{p} = 0.87, \emph{Figure \ref{fig:vel-1}}, left). The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings (legato parts) was not normally distributed (\emph{p} = 0.002). A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r(46)} = .03, \emph{p} = 0.84).

@@

For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r(46)} = -.26, \emph{p} = 0.071, From Staccato to Legato; \emph{r(46)} = -.19, \emph{p} = 0.21, \emph{Figure \ref{fig:vel-diff-1}}, left). The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings (transition points from legato to staccato) was not normally distributed (\emph{p} = 0.007). A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for the transition points from legato to staccato and participants' judgments as teaching (\emph{r(46)} = -.23, \emph{p} = 0.12).

@@

As Experiment 1, a Pearson product-moment correlation coefficient was computed by default for correlation analysis and a Spearman's rank correlation coefficient was additionally computed if normality assumption was violated based on the Shapiro-Wilk normality test.

@@

However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (\emph{p} = 0.080). A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (\emph{r(34)} = .29, \emph{p} = 0.091), suggesting that we need to be careful about the interpretation of the relationship between the performance tempi of dynamics recordings and participants' judgments as teaching.

@@

As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-2}}, right). Specifically, performances with louder forte (\emph{r(34)} = .45, \emph{p} = 0.007) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.006) were more likely to be judged as teaching. The Shapiro-Wilk normality test revealed that the distribution of KV values for dynamics recordings was not normally distributed (Forte; \emph{p} = 0.048, Piano' \emph{p} = 0.004). Spearman's rank correlation coefficient also confirmed that performances with louder forte (\emph{r(34)} = .43, \emph{p} = 0.010) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.013) were more likely to be judged as teaching.

@@

As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (\emph{Figure \ref{fig:vel-diff-2}}, right). Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r(34)} = -.75, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r(34)} = .59, \emph{p} \textless{} 0.001). The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; \emph{p} = 0.85, Piano to Forte; \emph{p} = 0.008). Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; \emph{r(34)} = -.73, \emph{p} \textless{} 0.001, Piano to Forte; \emph{r(34)} = .57, \emph{p} \textless{} 0.001).

>>>>

@@

@@

For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r(46)} = -.04, \emph{p} = 0.81, Piano; \emph{r(46)} = -.19, \emph{p} = 0.19, \emph{Figure \ref{fig:kot-1}}, right).

@@

For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r(46)} = .10, \emph{p} = 0.52, Staccato; \emph{r(46)} = -.02, \emph{p} = 0.87, \emph{Figure \ref{fig:vel-1}}, left).

@@

For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r(46)} = -.26, \emph{p} = 0.071, From Staccato to Legato; \emph{r(46)} = -.19, \emph{p} = 0.21, \emph{Figure \ref{fig:vel-diff-1}}, left).

@@

@@

@@

As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-2}}, right). Specifically, performances with louder forte (\emph{r(34)} = .45, \emph{p} = 0.007) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.006) were more likely to be judged as teaching.

@@

As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (\emph{Figure \ref{fig:vel-diff-2}}, right). Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r(34)} = -.75, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r(34)} = .59, \emph{p} \textless{} 0.001).
